---
title: "Assignment2"
author: "Shaoyang Zhuang"
date: "2023-10-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load packages


```{r cars}
# Install the packages if not already installed
if (!requireNamespace("Stat2Data", quietly = TRUE)) {
  install.packages("Stat2Data")
}

if (!requireNamespace("tidyverse", quietly = TRUE)) {
  install.packages("tidyverse")
}

# Load the packages
library(Stat2Data)
library(tidyverse)
data("Hawks")
head(Hawks)
```

## 1.Data Wrangling

This part is mainly about data wrangling. Basic concepts of data wrangling can be found in lecture 4.

## 1.1Select and filter

## 1.1 (Q1)
Use a combination of the select() and filter() functions to generate a data frame called “hSF” which
is a sub-table of the original Hawks data frame, such that

```{r pressure, echo=FALSE}
hSF<-Hawks %>% select(Species,Wing,Weight,Tail)%>%filter(Species=="RT"&Weight>=1)
head(hSF)
```
## 1.1 (Q2)

```{r}
num_obeservation<-nrow(hSF)
num_obeservation
num_variables<-ncol(hSF)
num_variables
```
## 1.2The arrange function
## 1.2(Q1)
```{r}
sort_hSF<-hSF%>%arrange(Wing)
head(sort_hSF)
```

## 1.3Join and rename functions
## 1.3(Q1)
```{r}
hawkSpeciesNameCodes<-data.frame(
   species_code=c("CH", "RT", "SS"),
   species_name_full=c("Cooper's", " Red-tailed", " Sharp-shinned")
)
head(hawkSpeciesNameCodes)

```

## 1.3(Q2)
```{r}
hawksFullName <- left_join(Hawks, hawkSpeciesNameCodes, by = c("Species" = "species_code"))%>%select(species_name_full,Wing,Weight,Tail)
head(hawksFullName, n=7)

```

## 1.4(Q1)
```{r}
hawksWithBMI<-Hawks%>%mutate(`Bird-BMI` =(Weight/(Wing^2))*1000)%>%select( Species ,`Bird-BMI`)%>%arrange(desc(`Bird-BMI`))
head(hawksWithBMI,n=8)

````


## 1.5(Q1)
```{r}
summary_table<-hawksFullName%>%group_by(species_name_full)%>%summarise(num_rows=n(),mn_wing=mean(Wing), md_wing=median(Wing), t_mn_wing=mean(Wing,trim=0.1), b_wt_ratio=max(Wing/Tail)
)
summary_table
```





## 1.5(Q2)
```{r}


hawksFullName <- left_join(Hawks, hawkSpeciesNameCodes, by = c("Species" = "species_code"))%>%select(species_name_full,Wing, Weight, Culmen, Hallux, Tail, StandardTail, Tarsus,  Crop)
summary_table2<-hawksFullName%>%group_by(species_name_full)%>%summarise(Wing=sum(is.na(Wing)),Weight=sum(is.na(Weight)),Culmen=sum(is.na(Culmen)),Hallux=sum(is.na(Hallux)),Tail=sum(is.na(Tail)),StandardTail=sum(is.na(StandardTail)),Tarsus=sum(is.na(Tarsus)),Crop=sum(is.na(Crop)))
summary_table2
```







## 1.2(Q1)## 1.2The arrange function
## 1.2(Q1)## 1.2The arrange function
## 1.2(Q1)## 1.2The arrange function
## 1.2(Q1)## 1.2The arrange function
## 1.2(Q1)## 1.2The arrange function
## 1.2(Q1)