---
title: "Assignment2"
author: "Shaoyang Zhuang"
date: "2023-10-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load packages


```{r cars}
# Install the packages if not already installed
if (!requireNamespace("Stat2Data", quietly = TRUE)) {
  install.packages("Stat2Data")
}

if (!requireNamespace("tidyverse", quietly = TRUE)) {
  install.packages("tidyverse")
}

# Load the packages
library(Stat2Data)
library(tidyverse)
data("Hawks")
head(Hawks)
```

## 1.Data Wrangling

This part is mainly about data wrangling. Basic concepts of data wrangling can be found in lecture 4.

## 1.1Select and filter

## 1.1 (Q1)
Use a combination of the select() and filter() functions to generate a data frame called “hSF” which
is a sub-table of the original Hawks data frame, such that

```{r pressure, echo=FALSE}
hSF<-Hawks %>% select(Species,Wing,Weight,Tail)%>%filter(Species=="RT"&Weight>=1)
head(hSF)
```
## 1.1 (Q2)

```{r}
num_obeservation<-nrow(hSF)
num_obeservation
num_variables<-ncol(hSF)
num_variables
```
## 1.2The arrange function
## 1.2(Q1)
```{r}
sort_hSF<-hSF%>%arrange(Wing)
head(sort_hSF)
```

## 1.3Join and rename functions
## 1.3(Q1)
```{r}
hawkSpeciesNameCodes<-data.frame(
   species_code=c("CH", "RT", "SS"),
   species_name_full=c("Cooper's", " Red-tailed", " Sharp-shinned")
)
head(hawkSpeciesNameCodes)

```

## 1.3(Q2)
```{r}
hawksFullName <- left_join(Hawks, hawkSpeciesNameCodes, by = c("Species" = "species_code"))%>%select(species_name_full,Wing,Weight,Tail)
head(hawksFullName, n=7)

```

## 1.4(Q1)
```{r}
hawksWithBMI<-Hawks%>%mutate(`Bird-BMI` =(Weight/(Wing^2))*1000)%>%select( Species ,`Bird-BMI`)%>%arrange(desc(`Bird-BMI`))
head(hawksWithBMI,n=8)

````


## 1.5(Q1)
```{r}
summary_table<-hawksFullName%>%group_by(species_name_full)%>%summarise(num_rows=n(),mn_wing=mean(Wing), md_wing=median(Wing), t_mn_wing=mean(Wing,trim=0.1), b_wt_ratio=max(Wing/Tail)
)
summary_table
```





## 1.5(Q2)
```{r}


hawksFullName <- left_join(Hawks, hawkSpeciesNameCodes, by = c("Species" = "species_code"))%>%select(species_name_full,Wing, Weight, Culmen, Hallux, Tail, StandardTail, Tarsus,  Crop)
summary_table2<-hawksFullName%>%group_by(species_name_full)%>%summarise(Wing=sum(is.na(Wing)),Weight=sum(is.na(Weight)),Culmen=sum(is.na(Culmen)),Hallux=sum(is.na(Hallux)),Tail=sum(is.na(Tail)),StandardTail=sum(is.na(StandardTail)),Tarsus=sum(is.na(Tarsus)),Crop=sum(is.na(Crop)))
summary_table2
```
## 2.1(Q1)
purrr包

## 2.1(Q2)
```{r}
impute_by_median<-function(x){
  mu<-median(x,na.rm=1)
  impute_f<-function(z){
    if(is.na(z)){
      return(mu)
    }else{
      return(z)
    }
  }
  return(map_dbl(x,impute_f))
}
v<-c(1,2,NA,4)
impute_by_median(v)

```



## 2.1(Q3)
```{r}
  x <- seq(0,10,by=0.1)
  y <- x * 5 + 1
  df_xy<-data.frame(x = x,y = y)
  head(df_xy,n=5)
```
## 2.1(Q4)

```{r}
df_xy%>%mutate(z=map2_dbl(x,y,~.x+.y))%>%head(5)
```

```{r}
sometimes_missing<-function(x,y){
  if(x%%5==0){
    return(NA)
  }else{
    return(y)
  }
}
sometimes_missing(14,25)
sometimes_missing(15,25)
```
```{r}
x<-seq(0,10,by=0.1)
y<-map2_dbl(1:101,x,~if(.x%%5==0)NA else 5*.y+1)
df_xy_missing <- data.frame(x=x,y=y)
df_xy_missing%>%head(10)
```
## 2.1(Q5)
```{r}
y<-impute_by_median(y)
resultQ5<-data.frame(x=x,y=y)
print(resultQ5)
```
## 2.2
```{r}
library(readxl) # load the readxl library
folder_path <- "D:/Desktop/firstRProject/"
#folder_path<-"C:/Users/" # set this to the name of the
# directory containing "HockeyLeague.xlsx"
file_name<-"HockeyLeague.xlsx" # set the file name
file_path<-paste(folder_path,file_name,sep="") # create the file_path
wins_data_frame<-read_excel(file_path,sheet="Wins") # read of a sheet from an xl file
wins_data_frame %>%
select(1:5)%>%
head(3)


```
## 2.2(Q1)
```{r}
library(dplyr)
library(tidyr)

# Assuming wins_data_frame is your original data frame

# Gather the data into a long format, separating Wins and Total
wins_tidy <- wins_data_frame %>%
  pivot_longer(cols = -...1, names_to = "Year", values_to = "Result") %>%
  separate(Result, into = c("Wins", "Total"), sep = " of ") %>%
  mutate(
    Team = as.character(...1),  # Convert Team to character
    Year = as.integer(Year),    # Convert Year to integer
    Wins = as.integer(Wins),    # Convert Wins to integer
    Total = as.integer(Total)  # Convert Total to integer
  ) %>%
  select(Team, Year, Wins, Total)  # Reorder the columns

# View the first few rows of wins_tidy to check the result
wins_tidy%>%head(5)
```
```{r}
wins_tidy %>% dim() 
```
## 2.2(Q2)
```{r}
losses_data_frame <- read_excel(file_path,sheet="Losses") # read of a sheet
losses_tidy <- losses_data_frame %>% 
  pivot_longer(cols = -...1, names_to = "Year", values_to = "Result")%>%
  separate(Result, into = c("Loss", "Total"), sep = "of")%>%
    mutate(
      Team = as.character(...1),
      Year = as.integer(Year),
      Loss = as.integer(Loss),
      Total = as.integer(Total)
    )%>%
    select(Team, Year, Loss, Total)
losses_tidy%>%head(5)
```
## 2.2(Q3)
```{r}
hockey_df <- wins_tidy %>%
  inner_join(losses_tidy, by= c("Team","Year", "Total"))%>%
  mutate(
    Draws = Total - Wins - Loss,
    Wins_rt = Wins/Total,
    Losses_rt = Loss/Total,
    Draws_rt = Draws/Total
  )%>%
  select(Team, Year, Wins, Total, Loss, Draws, Wins_rt, Losses_rt, Draws_rt)

hockey_df %>% head(5)


```
## 2.2(Q4)
```{r}
summary_df <- hockey_df %>% group_by(Team)%>%
  summarise(
    W_md = median(Wins_rt),
    W_mn = mean(Wins_rt),
    L_md = median(Losses_rt),
    L_mn = mean(Losses_rt),
    D_md = median(Draws_rt),
    D_mn = mean(Draws_rt)
  )%>%arrange(desc(W_md))
summary_df



```
## 3(Q1)
```{r}
library(ggplot2)

# Assuming wins_tidy is your data frame
wins_ducks <- wins_tidy %>%
  filter(Team == "Ducks")  # Filter for Ducks team

# Create a histogram plot with bin widths of 3
ggplot(wins_ducks, aes(x = Wins)) +
  geom_histogram(binwidth = 3, fill = "red", color = "black", alpha = 0.7) +
  labs(
    title = "Histogram of Wins for Ducks",
    x = "Wins",
    y = "Frequency"
  )


```

## 3(Q2)
```{r}
# Assuming wins_tidy is your data frame
ggplot(wins_tidy, aes(x = Wins)) +
  geom_density(adjust = 0.5, fill = "blue", alpha = 0.7) +
  geom_density(adjust = 2, fill = "red", alpha = 0.7) +
  labs(
    title = "Density Plot of Wins for Ducks",
    x = "Wins",
    y = "Density"
  ) +
  scale_fill_manual(values = c("blue", "red"))

```


## 3(Q3)
```{r}
library(dplyr)
library(tidyr)

# Assuming wins_tidy is your data frame
wins_teams <- wins_tidy %>%
  select(Year, Team, Wins) %>%
  pivot_wider(names_from = Team, values_from = Wins)

# View the wins_teams data frame
head(wins_teams)
```
```{r}
library(ggplot2)

# Create the scatter plot
ggplot(wins_teams, aes(x = Ducks, y = Eagles)) +
  geom_point() +
  labs(
    title = "Wins of Ducks vs. Wins of Eagles",
    x = "Wins of Ducks",
    y = "Wins of Eagles"
  )
```