---
title: "Assignment3"
author: "Shaoyang Zhuang"
date: "2023-10-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##1

```{r }
library(tidyverse)
library(Stat2Data)
data("Hawks")
head(Hawks)

```



## 1.1(Q1)
```{r}
HawksTail<-Hawks$Tail
head(HawksTail)
sample_mean <- mean(HawksTail)
cat("mean is ", sample_mean, "\n")
sample_median <- median(HawksTail)
cat("median is ",sample_median,"\n")
```
## 1.2(Q1)
```{r}
result <- Hawks %>% summarise(
  wing_mean<-mean(Wing, na.rm = TRUE),
  Wing_t_mean<-mean(Wing, trim = 0.5, na.rm = TRUE),
  Wing_med<-median(Wing, na.rm = TRUE),
  Weight_mean<-mean(Weight, na.rm = TRUE),
  Weight_t_mean<-mean(Weight, trim = 0.5, na.rm = TRUE),
  Weight_med<-median(Weight, na.rm = TRUE)
)
print(result)
```

## 1.2(Q2)
```{r}
result <- Hawks %>%
  group_by(Species) %>%
  summarize(
  wing_mean<-mean(Wing, na.rm = TRUE),
  Wing_t_mean<-mean(Wing, trim = 0.5, na.rm = TRUE),
  Wing_med<-median(Wing, na.rm = TRUE),
  Weight_mean<-mean(Weight, na.rm = TRUE),
  Weight_t_mean<-mean(Weight, trim = 0.5, na.rm = TRUE),
  Weight_med<-median(Weight, na.rm = TRUE)
  )
# Print the result
print(result)
```

## 1.3(Q1)
```{r}
a = 2
b = 3
result1 <- mean(HawksTail*a + b)
result2 <- a*mean(HawksTail) + b
result1
result2
```

## 1.3(Q2)
```{r}
a = 2
b = 3
result1 <- var(HawksTail*a + b)
result2 <- sd(HawksTail)
result1
result2

```


## 1.3(Q3)
```{r}

```











## 1.4
```{r}
hal<-Hawks$Hallux # Extract the vector of hallux lengths
hal<-hal[!is.na(hal)] # Remove any nans
outlier_val<-100
num_outliers<-10
corrupted_hal<-c(hal,rep(outlier_val,times=num_outliers))
mean(hal)
mean(corrupted_hal)
```
## 1.4
```{r}
num_outliers_vect <- seq(0,1000)
means_vect <- c()
for(num_outliers in num_outliers_vect){
  corrupted_hal <- c(hal,rep(outlier_val,times=num_outliers))
  means_vect <- c(means_vect, mean(corrupted_hal))
}
```
## 1.4(Q1)
```{r}
medians_vect <- c()

for( i in num_outliers_vect){
  corrupted_hal <- c(hal, rep(outlier_val, times = i ))
  medians_vect <- c(medians_vect, mean(corrupted_hal))
}

```
## 1.4(Q2)
```{r}
# Define the trim fraction q
q <- 0.1

# Create vectors to store medians and trimmed means
medians_vect <- c()
t_means_vect <- c()

# Loop through different numbers of outliers
for(i in num_outliers_vect) {
  # Create a vector with i - 1 outliers
  
  
  # Combine the outliers with the original data
  corrupted_hal <- c(hal, rep(outlier_val, times = i ))
  
  # Calculate the median and add it to the medians vector
  medians_vect <- c(medians_vect, median(corrupted_hal))
  
  # Calculate the trimmed mean with trim fraction q and add it to the t_means vector
  t_means_vect <- c(t_means_vect, mean(corrupted_hal, trim = q))
}

# Now you have two vectors: medians_vect and t_means_vect

```

## 1.4(Q3)
```{r}
df_means_medians <- data.frame(num_outliers=num_outliers_vect, mean=means_vect,
t_mean=t_means_vect, median=medians_vect)



df_means_medians %>%
pivot_longer(!num_outliers, names_to = "Estimator", values_to = "Value") %>%
ggplot(aes(x=num_outliers,color=Estimator, linetype=Estimator,y=Value)) +
geom_line()+xlab("Number of outliers")
```
## 1.5(Q1)
```{r}
library(ggplot2)
library(dplyr)

# Assuming you have loaded your "Hawks" data frame

# Group the data by "Species"
hawk_data <- Hawks %>%
  group_by(Species)

# Now, let's create the box plot
ggplot(hawk_data, aes(x = Species, y = Weight)) +
  geom_boxplot(fill = "white") +
  labs(
    title = "Distribution of Hawk Weights by Species",
    x = "Species",
    y = "Weight"
  )


```

## 1.5(Q2)
```{r}

library(dplyr)

# Group the data by "Species" and calculate quantiles
quantiles_data <- Hawks %>%
  group_by(Species) %>%
  summarize(
    Q1 = quantile(Weight, 0.25, na.rm = TRUE),
    Median = median(Weight, na.rm = TRUE),
    Q3 = quantile(Weight, 0.75, na.rm = TRUE)
  )
quantiles_data
```
## 1.5(Q3)
```{r}
num_outliers <- function(sample_data){
    sample_data <- sample_data[!is.na(sample_data)]
    Q1 = quantile(sample_data, 0.25)
    Q2 = quantile(sample_data, 0.75)
    IQR = Q2 - Q1
    X1 = Q1 - 1.5 * IQR
    X2 = Q2 + 1.5 * IQR
    x = 0
    for(i in sample_data){
      if(i < X1 | i > X2){
        x = x + 1
       # print(i)
      }
    }
   # num_outliers <- sum(sample_data < X1 | sample_data > X2)
  return(x)
  }
num_outliers(c(0, 40,60,185))
```
## 1.5(Q4)
```{r}
outliers_summary <- Hawks %>%
  group_by(Species) %>%
  summarise(num_outliers_weight = num_outliers(Weight))

# Print the result
print(outliers_summary)

```
## 1.6(Q1)
```{r}
# Compute the covariance between Weight and Wing
cleaned_data <- na.omit(Hawks)
covariance <- cov(cleaned_data$Weight, cleaned_data$Wing)
cat("Covariance between Weight and Wing:", covariance, "\n")

# Compute the correlation between Weight and Wing
correlation <- cor(cleaned_data$Weight, cleaned_data$Wing)
cat("Correlation between Weight and Wing:", correlation, "\n")
```
## 1.6(Q2)
```{r}
a = 2.4
b = 7.1
c = -1
d = 3
# Create new variables by applying the transformation
cleaned_data$Weight_transformed <- a * cleaned_data$Weight + b
cleaned_data$Wing_transformed <- c * cleaned_data$Wing + d
# Compute the covariance between the transformed variables
covariance_transformed <- cov(cleaned_data$Weight_transformed, cleaned_data$Wing_transformed)
# Print the result
cat("Covariance between transformed Weight and transformed Wing:", covariance_transformed, "\n")

correlation_transformed <- cor(cleaned_data$Weight, cleaned_data$Wing)

cat("correlation between transformed Weight and transformed Wing:", correlation_transformed, "\n")



```

## 2.1(Q1)
a random experiment is a process with uncertain outcomes, the sample space is the set of all possible outcomes, and events are subsets of the sample space that describe specific occurrences or observations. These concepts are fundamental to the study of probability and statistics and are used to model and analyze uncertainty and randomness in various real-world situations.

## 2.1(Q2)

The event is that the sum of twice dice is 7.

E = {(1, 6), (2, 5), (3, 4), (4, 3), (5, 2), (6, 1)}

there are a lot of events. We can't list them totally

Yes.

## 2.2(Q1)

1.
A ∪ B = {1, 2, 3, 4, 6}
A ∪ C = {1, 2, 3, 4, 5, 6}

2.
A ∩ B = {2}
A ∩ C = ∅

3.
A\B = {1, 3}
A\C = {1, 2, 3}

4.
No
Yes

5.
Yes

6.
{1, 2, 3} and {4, 5, 6}
{1, 2}, {3, 4}, and {5, 6}


## 2.2(Q3)

|E| = 2^k

## 2.2(Q4)
1.
∅
2.
S1   ∪    S2     ∪      S3        ∪   S4


## 3(Q3)
```{r}

# Load the ggplot2 and dplyr libraries if not already loaded
library(ggplot2)
library(dplyr)

# Assuming you have the "Hawks" dataset
# Replace 'your_data' with the actual dataset name

# Group the data by the "Species" column
Hawks_grouped <- Hawks %>%
  group_by(Species)

# Create the scatter plot with different colors for each species
ggplot(data = Hawks_grouped, aes(x = Tail, y = Weight, color = Species)) +
  geom_point() +
  labs(x = "Tail", y = "Weight") +
  ggtitle("Scatter Plot of Tail vs. Weight for Hawks")

```

## 3(Q4)
```{r}
# Load the ggplot2 and dplyr libraries if not already loaded
library(ggplot2)
library(dplyr)

# Assuming you have the "Hawks" dataset
# Replace 'your_data' with the actual dataset name

# Group the data by the "Species" column
Hawks_grouped <- Hawks %>%
  group_by(Species)

# Create the scatter plot with trend lines and facets
ggplot(data = Hawks_grouped, aes(x = Tail, y = Weight, color = Species)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, fullrange = TRUE) +  # Add trend lines
  labs(x = "Tail", y = "Weight") +
  ggtitle("Scatter Plot with Trend Lines for Hawks") +
  facet_wrap(~ Species, scales = "free")


```

## 3(Q5)
```{r}
library(ggplot2)
library(dplyr)

# Assuming you have the "Hawks" dataset
# Replace 'your_data' with the actual dataset name

# Group the data by the "Species" column
Hawks_grouped <- Hawks %>%
  group_by(Species)

# Create the scatter plot with trend lines and facets, and different colors
plot <- ggplot(data = Hawks_grouped, aes(x = Tail, y = Weight, color = Species)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, fullrange = TRUE) +  # Add trend lines
  labs(x = "Tail", y = "Weight") +
  ggtitle("Scatter Plot with Trend Lines for Hawks")

# Identify the rows with the heaviest hawks within each species
heaviest_hawks_data <- Hawks_grouped %>%
  filter(Weight == max(Weight))

# Add the annotation for the heaviest hawk within each species
highlighted_points <- plot +
  geom_text(data = heaviest_hawks_data, aes(x = Tail, y = Weight, 
            label = paste("Heaviest Hawk\nWeight:", max(Weight))), 
            hjust = 1.5, vjust = 0, size = 4, color = "black") +
  geom_point(data = heaviest_hawks_data, aes(x = Tail, y = Weight, color = Species), size = 3)

print(highlighted_points)

```